### 2020-03-08 Common/chapters/conclusions.tex
Johan and Julien: minors

Then, the work focused on overcoming one of the main issues in deep learning: the lack of data. To achieve this, transfer learning, as well as more common techniques such as data augmentation, were applied. Our transfer learning implementation alternated between frozen and unfrozen steps and made use of brain and lung datasets to increase the model performance on a prostate dataset. During frozen steps, the first part of the model (the feature extractor) does not update its weights at all, whereas the second part (the decision maker) does. Experiments showed that showed that our method allowed to increase the AUC on our test set by approximately 18\%, from $0.68$ before transfer learning to $0.80$ after transfer learning. Since a less-experienced radiologist can aim for an AUC of $0.81$~\cite{42}, this model could serve as a second diagnosis. These results could even be improved with another model, another way of processing data, etc.

>>>>

Then, the work focused on overcoming one of the main issues in deep learning: the lack of data. To achieve this, transfer learning, as well as more common techniques such as data augmentation, were applied. Our transfer learning implementation alternated between frozen and unfrozen steps and made use of brain and lung datasets to increase the model performance on a prostate dataset. During frozen steps, the first part of the model (the feature extractor) does not update its weights at all, whereas the second part (the decision maker) does. Experiments showed that our method allowed to increase the AUC on our test set by approximately 18\%, from $0.68$ before transfer learning to $0.80$ after transfer learning. Since a less-experienced radiologist can aim for an AUC of $0.81$~\cite{42}, this model could serve as a second diagnosis. These results could even be improved with another model, another way of processing data, etc.
